Q\&A Plataforms, or question and answer platforms are currently very popular applications that allow your users to share Knowledge itself
 through questions and answers. These platforms serve as an online source for users to find Quick and efficient objective answers to your
 questions. Many such applications have come up with their content focused on programming. Answered questions and sample codes help
 developers troubleshoot problems and obstacles on developer day.

Design Patterns are general solutions applied to object-oriented programming that address recurring problems in a given context in software design.
 A design pattern is not a code ready to take advantage of an application but a template to solve a problem being solutions that have already been
 used and tested during the time that gives us confidence in its effectiveness. The use of these standards bring many benefits to software design,
 such as facilitating maintenance, improving documentation, making software reusable among others. The big problem with using Design Patterns is
 that most of the time it is necessary to be an experienced developer for application of a given standard.

Aiming at the popularity and efficiency of Q\&A Social platforms in assisting programmers with their doubts and the difficulty in using Desgin Patterns
 by not so experienced programmers, we propose the creation of a smartphone application, in the model of platforms Q\&A, The e-Design Patterns.
 An application to help and accelerate the learning process to use Design Patterns using the strategies and features of these platforms to create a successful application.